\documentclass{resume}
\usepackage{url}
\usepackage{hyperref}
\renewcommand{\categoryfont}{\sc}
\setlength{\oddsidemargin}{0.7in}
\setlength{\marginparwidth}{1.1in}\addtolength{\marginparwidth}{-\marginparsep}
 \setlength{\evensidemargin}{\oddsidemargin}
 \setlength{\textwidth}{\paperwidth}
 \addtolength{\textwidth}{-2.5in}
 \addtolength{\textwidth}{-1.7\oddsidemargin}
 \addtolength{\textwidth}{\marginparwidth}
 \addtolength{\textwidth}{\marginparsep}
\setlength{\topmargin}{-0.7in}
\addtolength{\textheight}{-1.5cm}
\renewcommand{\labelcitem}{$\diamond$}
\renewcommand{\labelitemi}{$\cdot$}
\newcommand{\first}{$\mbox{1}^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$\mbox{2}^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$\mbox{3}^{\mbox{\scriptsize rd}}$\ }
\newcommand{\fourth}{$\mbox{4}^{\mbox{\scriptsize th}}$\ }
\newcommand{\fifth}{$\mbox{5}^{\mbox{\scriptsize th}}$\ }
\newcommand{\seventh}{$\mbox{7}^{\mbox{\scriptsize th}}$\ }
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}
\author{Ali Khodagholi}

% ------ Address --------------------------------------------------------
\address{
\href{https://www.linkedin.com/in/ali-khodagholi-455906119/}{LinkedIn}\\
\href{https://scholar.google.com/citations?user=bcqqPZoAAAAJ&hl=en&oi=ao}{Google Scholar}\\
\href{https://github.com/ali-khodagholi}{GitHub}
}
        {Cell Phone: +98-912-4784996\\
      Email: \href{mailto:akhodagholi1@gmail.com}{akhodagholi1 [at] gmail.com}
      
      }
\def\shr{Iran University of Science and Technology}
\begin{document}
\maketitle
\vspace{-0.5cm}
% ------- Research Interests ---------------------------------------------------
\begin{category}{Research Interests}
\citembullet Climate Change and Adaption Agriculture
\citembullet Multi-Objective Optimization
\citembullet Water Resources Planning and Management
\citembullet Crop Simulation Model
\end{category}
\vspace{0.1cm}
% ------- Education ---------------------------------------------------
\begin{category}{Education}
\citembullet Iran University of Science and Technology, Tehran, Iran
\hfill
(2018 - 2021)\\
Master of Science in Water Resources Management\\
Overall GPA: {\small 18.92/20 (3.88/4.00)}\\
{\textbf{Thesis Topic:}}
{\small Impacts of Climate Change on Irrigation Scheduling for Crops: Case Study Potato}\\
{\textbf{Advisers:}}
{\small Prof. Abbas Afshar, and Dr. Saeed Soufizadeh}\smallskip\\
- Calibration of the SUBSTOR-Potato using GLUE model\\
- Generating future climate data using LARS-WG\\
- Simulation and optimization of crop growth using the DSSAT model\\
- Finding an optimum trade-off between water and nitrogen resources using meta-heuristic algorithm
\\
\citembullet Iran University of Science and Technology, Tehran, Iran
\hfill
(2014 - 2018)\\
Bachelor of Science in Civil Engineering\\
Overall GPA: {\small 16.68/20 (3.41/4.00)}\\
{\textbf{Thesis Topic:}}
{\small Multi-objective optimization for sustainable groundwater management}\\
{\textbf{Advisers:}}
{\small Prof. Abbas Afshar}
\end{category}
\vspace{0.1cm}
% ---------Hoors and Awards -------------------------------------------------------
\begin{category} {Honors \& Awards}
\citembullet Ranked within the Top 1\% among approximately 250,000 participants in the National Entrance Exam for Iranian universities
\hfill (2014)
\citembullet Ranked within the top 20\% among students of Civil Engineering at the end of Bachelor's degree, Iran University of Science and Technology.
\hfill (2018)
\citembullet Direct master of science at IUST accepted as a highly ranked student
\hfill (2018)
\citembullet Ranked \textbf{1st} in the M.Sc. Water Resources Management - Iran University of Science and Technology
\hfill (2021)
\end{category}
\vspace{0cm}
% ---------  Publications-------------------------------------------------------
\begin{category} {Publications}
\citembullet Abbas Afshar, Mohamad Amin Tavakoli, and \textbf{Ali Khodagholi}. "Multi-Objective Hydro-Economic Modeling for Sustainable Groundwater Management", Water Resources Management, \\
DOI: \href{https://doi.org/10.1007/s11269-020-02533-4}{10.1007/s11269-020-02533-4}
\hfill (Cited by: 18)
\citembullet Ali Kaveh, Pouya Almasi, and \textbf{Ali Khodagholi}. "Optimum design of castellated beams using four recently developed meta-heuristic algorithms", Iranian Journal of Science and Technology, Transactions of Civil Engineering, DOI: \href{https://doi.org/10.1007/s40996-022-00884-z}{10.1007/s40996-022-00884-z}
\hfill (Cited by: 11)
\citembullet \textbf{Ali Khodagholi}, Abbas Afshar , and Saeed Soufizadeh. "Optimization modeling of irrigation and nitrogen management under climate change for potato using SUBSTOR-Potato (DSSAT) model", under preparation.
\citembullet Mohammadmahdi Arabbafrani, \textbf{Ali Khodagholi}, and Reza Kerachian . "A Framework for Seasonal Groundwater Banking: A Case Study", under submission.
\end{category}
\vspace{0.7cm}
% --------- Academic Projects -------------------------------------------------------
\begin{category} {Academic Projects}
\citembullet Soil-crop dynamic simulation based on FAO using MATLAB
\citembullet Water allocation of reservoir and river system simulation using WEAP
\citembullet Optimizing reservoir operation using Lingo
\citembullet Prediction of flood hydrograph using HEC-HMS
\citembullet Finding flood zones for flood management using HEC-RAS and ArcGIS
\citembullet Calculation of soil erosion based on RUSLE model using ArcGIS and ENVI
\end{category}
\vspace{0cm}
% --------- Teaching Experience -------------------------------------------------------
\begin{category} {Teaching Experience}
\citembullet Teaching Assistant of Water Resources System Analysis and Management (2019) for Dr. Alizadeh.
\citembullet Teaching Assistant of Engineering Hydrology (2018 - 2019) for Dr. Zahabiyoun.
\citembullet Teaching Assistant of Mechanic of Material (2017 - 2018) for Dr. Ghaderi.
\citembullet Teaching Assistant of Concrete Technology (2016) for Dr. Famili.
% \citembullet Teaching Assistant of Programming (C++) (2016) for Dr. Torkashvan.
\end{category}
\vspace{0cm}
% --------- Selected Courses -------------------------------------------------------
\begin{category} {Selected Courses}
\citembullet Water Resources Systems Analysis and Management
\hfill 20/20
\\ Instructor: Dr. Alizadeh
\citembullet Advanced Engineering Hydrology 
\hfill 19.25/20
\\ Instructor: Dr. Zahabiyoun
\citembullet Flood and Drought Management 
\hfill 19.2/20
\\ Instructor: Prof. Afshar
\citembullet Risk, Uncertainty and Reliability Analysis 
\hfill 20/20
\\ Instructor: Dr. Alizadeh
\citembullet Application of RS and GIS in Civil Engineering
\hfill 18.5/20
\\ Instructor: Dr. Mojaradi
\end{category}
\vspace{0cm}
% --------- Technical Skills -------------------------------------------------------
\begin{category} {Technical Skills}
\citembullet Expert in Programming with MATLAB, Python, C++, and Visual Basic.
\citembullet Expert in Water Resources and Agriculture Software: WEAP, ArcGIS, HEC-HMS, Lingo, DSSAT, and LARS-WG.
\citembullet Fully familiar with Soft Computing, Meta-heuristic Optimization, and Crop Simulation Models.
\end{category}
\vspace{0cm}
% --------- Language Skills -------------------------------------------------------
\begin{category} {Language Skills}
\citembullet {\textbf{Persian:}} Native
\citembullet {\textbf{TOEFL:}} 99
\citembullet {\textbf{GRE:}} General test will be taken on November 20th, 2023
\end{category}
\vspace{0cm}
% --------- Work Experience -------------------------------------------------------
\begin{category} {Work Experience}
\citembullet Founder and Programmer of Online Game
\hfill (2021 - up to now)
\citembullet Designer in Mahab Ghods, Water Reservoir Projects in Tabriz and Zanjan
\hfill (2017)
\citembullet Head of the Scientific Society of Civil Engineering at Iran University of Science and Technology, Tehran, Iran
\hfill (2016 - 2017)
\citembullet Editor-in-chief in Cement and Concrete Journal at at Iran University of Science and Technology, Tehran, Iran
\hfill (2015 - 2016)
\end{category}
\vspace{0cm}
% --------- References -----------------------------------------------
% \begin{category} {References}
% \citembullet Prof. Abbas Afshar
% (Professor) Department of Civil Engineering, Iran University of Science and Technology, Tehran, Iran. Email:
% \href{mailto:a_afshar@iust.ac.ir}{\textit{a\_afshar@iust.ac.ir}} 
% \citembullet Prof. Abbas Ghaderi
% (Professor) Department of Civil Engineering, Iran University of Science and Technology, Tehran, Iran. Email:
% \href{mailto:Ghaheri@iust.ac.ir}{\textit{Ghaheri@iust.ac.ir}} 
% \citembullet Dr. Hossein Alizadeh
% (Assistant  Professor) Department of Civil Engineering, Iran University of Science and Technology, Tehran, Iran. Email:
% \href{mailto:Alizadeh@iust.ac.ir}{\textit{Alizadeh@iust.ac.ir}}
% \citembullet Dr. Bagher Zahabiyoun
% (Associate Professor) Department of Civil Engineering, Iran University of Science and Technology, Tehran, Iran. Email:
% \href{mailto:Bagher@iust.ac.ir}{\textit{Bagher@iust.ac.ir}}
% \end{category}
%---------------------------------------------------------------
\end{document}
